---
title: "Installing GAPIT"
output: rmarkdown::html_vignette
description: >
  Steps to follow to successfully use all of GAPIT's functionality./ 
vignette: >
  %\VignetteIndexEntry{dplyr <-> base R}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4, tibble.print_max = 4)

knitr::opts_chunk$set(eval=FALSE)
```


A few tips and tricks for installing GAPIT. You can skip these steps and try to run this:

```{r}
remotes::install_github("jiabowang/GAPIT", force=TRUE)
library(GAPIT)
```

If you do not have {remotes} installed, then install it first: 
```{r}
install.packages("remotes")
```

If you are able to load the GAPIT library, congratulations! If not, read and implment the following instructions.


## Windows Users

Install [RTools](https://cran.r-project.org/bin/windows/Rtools/). 

GAPIT needs to be compiled. Mac and Linux systems already have C compilers installed on their systems, but Windows systems often do not. You may need to install [RTools](https://cran.r-project.org/bin/windows/Rtools/) to access a C compiler (that is configured to work with R). RTools is a program, not a package, so follow the link and read the instructions for download and installation. 

## Everyone 


Several accessory packages are used by GAPIT that must be downloaded from [Bioconductor](https://www.bioconductor.org/) and GitHub. 

### Install Bioconductor Packages


1. Install Bioconductor:
```{r}
install.packages("BiocManager")
```

1. Install [snpStats](https://www.bioconductor.org/packages/release/bioc/html/snpStats.html) & [multtest](https://www.bioconductor.org/packages/release/bioc/html/multtest.html) from Bioconductor: 
```{r}
BiocManager::install("snpStats")
BiocManager::install("multtest")
```

### Install GitHub packages

The package {LDheatmap} must be installed from [GitHub](https://github.com/SFUStatgen/LDheatmap) since it is currently not on CRAN. 
```{r}
remotes::install_github("SFUStatgen/LDheatmap")
```

## Install GAPIT

```{r}
remotes::install_github("jpiaskowski/GAPIT",force=TRUE)
library(GAPIT)
```


